---
title: "The Tidy Text Format"
author: "Clinton moshe"
date: "11/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Tidy data principles is a powerful way to make handling data in an easier way especially when dealing with text data types. As described by
Hadley Wickham (Wickham 2014), tidy data has a specific structure: Each variable is a column, Each observation is a row and Each type of observational unit is a table.


```{r cars}
text <- c("Because I could not stop for Death -",
          "He kindly stopped for me -",
          "The Carriage held but just Ourselves -",
          "and Immortality")
text
```
## Converting text to a tidy format
```{r}
library(dplyr)
library(tibble)
text_df <- data_frame(line = 1:4, text = text)
text_df
```
## tokenization
```{r}
library(tidytext)
text_df %>% 
  unnest_tokens(output=word, input=text)
```
## Tidying the Works of Jane Austen
```{r}
library(janeaustenr)
library(stringr)
original_books <- austen_books() %>%
  # adding two new columns linenumber and chapter
    group_by(book) %>% mutate(linenumber = row_number(),
    chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
    ignore_case = TRUE)))) %>%  ungroup()
as_tibble(original_books)
```
## Tokenizing the text
```{r}
tidy_books = original_books %>%
              unnest_tokens(output = word, input = text)
tidy_books
# COUNTING THE FREQUENCY OF THE WORDS
tidy_books %>% 
  count(word, sort = TRUE)
```
## Removing stop words e.g the, of , to etc
```{r}
data("stop_words")
stop_words
# removing stop words
tidy_books = tidy_books %>% 
              anti_join(stop_words)
tidy_books

# counting the most common words
tidy_books %>% 
      count(word, sort = TRUE)
# counting the most common books
tidy_books %>% 
      count(book, sort = TRUE)
# counting the number of chapters
tidy_books %>% 
      count(chapter, sort = FALSE)
```
## Visualizing the most common words
```{r}
library(ggplot2)
tidy_books %>%
  count(word, sort = TRUE) %>%
  filter(n > 600) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill='blue') +  xlab(NULL) + 
  coord_flip() + ggtitle('Most common used words')
```
## Gutenbergr package


## test chunk
```{r}
library(tidyverse)
library(janeaustenr)
janeaustenr::austen_books()[1:100,]
austen_books() %>% group_by(book) %>% summarise(total_lines=n())
# view(emma)
```

